Automated verification of stand-alone solar photovoltaic systems

### 2018-11-22 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%------------------------------------------
\subsection{Results}
\label{sec:results_indeed}
%------------------------------------------
%
%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel. This verification took approximately 63.3 hours to be performed. Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on); this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but we have found flaws related to the battery autonomy, when SOC reached a empty-battery level. Our verification engine identified those flaws (for all four houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries. Our verification engine took approximately 409.3 hours to find this flaw in house 1; 611.2 hours for house 2; 615.8 hours for house 3, and 620.8 hours for house 4. These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a mouth is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of~\ref{table:controller}; and after the sun rises, the systems returns to normal condition operation.

The same five case studies were evaluated by HOMER Pro. The result of simulation shows that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed with HOMER Pro.

Despite the divergence of results for the houses 1, 2, 3 and 4, comparing our automated tool with HOMER Pro, it is evident that the information collect from the dweller shows that the automated verification has the correct evaluation of the PV system. House 5 presented flaws from both tools, however only the automated verification showed which system project error was responsible for the flaw (number of PV panels).

It is worth to mention that a PV design always uses daily average values of sun hours to each site, with impact at the PV components. Those hours are based on historic data and, in field, it is not unusual to find days where that number of hours was not reached, because of weather. The season has impact, as the fact that the case studies are from the Rain Forest, where the clouds are always present. With that in mind, the identified flaws at houses 1, 2, 3, and 4, are justified once again.
%
%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed.
%
%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.

>>>>

%------------------------------------------
\subsection{Results}
\label{sec:results_indeed}
%------------------------------------------
%
%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
The description of our experimental results can be broken down into two parts: (a) the 1,200 W PV system (house 5) failed during the sizing check since the number of panels was \textit{incorrectly} sized; in particular, the counterexample provided by our verification engine indicated 3 PV panels in parallel and the actual project has 2 in series and 2 in parallel. This verification took approximately 63.3 hours to be performed. Surveying the owner of the 1,200 W system we identified that, in fact, the system does not meet the battery autonomy most of the time (mainly when all loads are turned on); this behavior is expected since the system was purchased as an off-the-shelf solution and not as a customized design for the electrical charges of the house; (b) For the 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during verification, but our verification engine has found flaws related to the battery autonomy, particularly when SOC reached a empty-battery level. Our verification engine identified those flaws (for all four houses) right after the first night-discharge cycle, i.e., before the solar system started to recharge the batteries. Our verification engine took approximately 409.3 hours to find this flaw in house 1; 611.2 hours for house 2; 615.8 hours for house 3, and 620.8 hours for house 4. These flaws were confirmed with the dwellers who own the systems by an interview process: at least once a mouth is usual the system to turn off, normally in raining or clouds days, thereby reaching the situation described in Step 3 of Table~\ref{table:controller}; after the sun rises, the systems returns to normal condition operation.

The same five case studies were evaluated by HOMER Pro. The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed by HOMER Pro.
%
Despite the divergence of results for the houses 1, 2, 3 and 4 w.r.t. our proposed approach, it is evident that the information collected from the dwellers indicate that our approach has the correct evaluation of the PV system. House 5 presented flaws from both tools; however, only our approach indicated which system project error was responsible for the flaw (number of PV panels).
%
Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components. Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions. The season has impact since the case studies are from the rain forest, where clouds are always present. As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
%
%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed.
%
%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.
